Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-04 methodology.tex
trivial tweak
make changes based on John's TODO for Section 3

We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \TODO{can we get a better cite?}. Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

@@

The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each containing eight routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. \TODO{What's the resulting router radix?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}. In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks. Due to our use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination. \TODO{Verify this. Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the \TODO{max? avg across ranks? distribution?} communication time.
\end{itemize}

Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach. We instead allow MPI communications to proceed as quickly as they are able. \TODO{is this a good enough explanation? Anything else we should add?}

>>>>

We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \NOTE{can we get a better cite? done}. Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

@@

The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. 
In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels. For each router, there could be $p = 4$ compute nodes attached to it via terminal links. The router has $h = 4$ global channels used as intergroup connections through which it connected to other routers in different groups. The radix of each router is $k = a+h+p-1 = 13$. 
The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. \NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } The dragonfly network aggregate bandwidth is 5.25 GiB/s for the local and terminal router-ports, 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} \NOTE{What are these bandwidths? done!}. In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks. Due to our use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination. \TODO{Verify this. Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the distribution of MPI ranks \NOTE{max? avg across ranks? distribution? done!} communication time.
\end{itemize}

Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach. We instead allow MPI communications to proceed as quickly as they are able. \TODO{is this a good enough explanation? Anything else we should add? sounds excellent to me!}
